Zero-Shot Task Adaptation by Homoiconic Meta-mapping (HoMM)

### 2019-12-05 writing/poster/HoMM_transferable_skills_poster.tex
Style tweaks and prior work

\begin{column}[t]{0.248\textwidth}
\begin{block}{\huge Intro: zero-shot adaptation}
\Large
\begin{itemize}
\item Humans can adapt zero-shot to novel tasks, based on their relationship to prior tasks.
\item For example, if asked to alter our behavior on a game we have learned (like trying to lose or achieve some other goal), we can perform well on our first try.
\item We take inspiration from this to propose \emph{meta-mapping}, a novel function-transformation perspective on zero-shot task performance.
\item We propose Homoiconic Meta-Mapping (HoMM) architectures as a parsimonious implementation of this framework.
\item We demonstrate successful zero-shot adaptation to related but substantially different tasks, such as adapting to trying to lose a card game the system has been trained to win.
\end{itemize}
\end{block}
\begin{block}{\huge Meta-mapping}
\Large
\begin{itemize}
\item Consider a functional perspective. Basic tasks can be seen as functions mapping images to classes, or states to actions, or card hands to bets.
\item We suggest it's then useful to think of transformations over functions, that is, functions which take other functions as input and/or output.
\item We call these higher-level functions \emph{meta-mappings}. They are functions which take basic functions as input and produce other basic functions as output.
\item For example, we could have a try-to-lose function which takes as input a function that tries to win money by betting, and outputs a function which tries to lose money by betting.
\item We suggest that these transformations of functions are a useful way to think about human flexibility.
\end{itemize}
\end{block}
\end{column}
\begin{column}[t]{0.496\textwidth}
\begin{block}{\huge Homoiconic Meta-Mapping (HoMM) architectures}
\begin{figure}[H]
\centering
\begin{tikzpicture}[scale=3, every node/.style={scale=1.2}]
%% basic meta learning
\begin{scope}[shift={(0.4, 0.4)}]
\draw[boundingbox, fill=white] (-3, -4.3) rectangle (2.5, 3.2);
\end{scope}
\begin{scope}[shift={(0.2, 0.2)}]
\draw[boundingbox, fill=white] (-3, -4.3) rectangle (2.5, 3.2);
\end{scope}

@@

\path [arrow, dashed, out=0, in=-90] ([xshift=-0.5]metaevalD2targs.east) to (metaevaldispatch.south);
\end{scope}
\path [arrow, line width=2mm, draw=bblue, dotted, out=-30, in=160] ([xshift=3,yshift=-3]metaoutputs.center) to ([xshift=2, yshift=-10]metaevalzfunc.north west);
\end{tikzpicture}
%\caption{The HoMM architecture allows for transformations at different levels of abstraction. (a) For basic meta-learning a dataset consisting of (input embedding, output embedding) tuples is processed by the meta-network \(\mathcal{M}\) to produce a function embedding \(z^{func}\), which is processed by the hyper network \(\mathcal{H}\) to parameterize a function \(F_{z^{func}}\), which attempts to compute the transformation on probe inputs (used to encourage the system to generalize). However, our approach goes beyond basic meta-learning. The function embedding \(z^{func}\) can then be seen as a single input or output at the next level of abstraction, when the same networks \(\mathcal{M}\) and \(\mathcal{H}\) are used to transform function embeddings based on examples of a meta-mapping (b). To evaluate meta-mapping performance, a probe embedding of a held-out function is transformed by the architecture to yield a predicted embedding for the transformed task. The performance of this predicted embedding is evaluated by moving back down a level of abstraction and evaluating on the actual target task (c). Because the function embedding is predicted by a transformation rather than from examples, new tasks can be performed zero-shot. (\(M\) and \(H\) are learnable deep networks, and $F_{z}$ is a deep network parameterized by $\mathcal{H}$ conditioned on function embedding \(z\). Input and output encoders/decoders are omitted for simplicity. See the text and Appendix \ref{app_model_details} for details.)} \label{architecture_inference_fig}
\end{figure}
\end{block}
\end{column}
\begin{column}[t]{0.248\textwidth}
\begin{block}{\huge Conclusions}
\end{block}
\end{column}
\end{columns}
\end{frame}
\end{document}

>>>>

\begin{column}[t]{0.248\textwidth}
\begin{block}{\huge Intro: zero-shot adaptation}
\begin{itemize}
\item Humans can adapt zero-shot to novel tasks, based on their relationship to prior tasks.
\item For example, if asked to alter our behavior on a game we have learned (like trying to lose or achieve some other goal), we can perform well on our first try.
\item We take inspiration from this to propose \emph{meta-mapping}, a novel function-transformation perspective on zero-shot task performance.
\item We propose Homoiconic Meta-Mapping (HoMM) architectures as a parsimonious implementation of this framework.
\item We demonstrate successful zero-shot adaptation to related but substantially different tasks, such as adapting to trying to lose a card game the system has been trained to win.
\end{itemize}
\end{block}
\begin{block}{\huge Meta-mapping}
\begin{itemize}
\item Consider a functional perspective. Basic tasks can be seen as functions mapping images to classes, or states to actions, or card hands to bets, etc.
\item We suggest it's then useful to think of transformations over functions, that is, functions which take other functions as input and/or output.
\item We call these higher-level functions \emph{meta-mappings}. They are functions which take basic functions as input and produce other basic functions as output.
\item For example, we could have a try-to-lose function which takes as input a function that tries to win money by betting, and outputs a function which tries to lose money by betting.
\item We suggest that meta-mappings are a useful way to think about human-like zero-shot adaptation.
\end{itemize}
\end{block}
\end{column}
\begin{column}[t]{0.496\textwidth}
\begin{block}{\huge Homoiconic Meta-Mapping (HoMM) architectures}
\begin{figure}[H]
\centering
\normalsize
\begin{tikzpicture}[scale=3, every node/.style={scale=1.2}]
%% basic meta learning
\begin{scope}[shift={(0.4, 0.4)}]
\draw[boundingbox, fill=white] (-3, -4.3) rectangle (2.5, 3.2);
\end{scope}
\begin{scope}[shift={(0.2, 0.2)}]
\draw[boundingbox, fill=white] (-3, -4.3) rectangle (2.5, 3.2);
\end{scope}

@@

\path [arrow, dashed, out=0, in=-90] ([xshift=-0.5]metaevalD2targs.east) to (metaevaldispatch.south);
\end{scope}
\path [arrow, line width=2mm, draw=bblue, dotted, out=-30, in=160] ([xshift=3,yshift=-3]metaoutputs.center) to ([xshift=2, yshift=-10]metaevalzfunc.north west);
\end{tikzpicture}
%\caption{The HoMM architecture allows for transformations at different levels of abstraction. (a) For basic meta-learning a dataset consisting of (input embedding, output embedding) tuples is processed by the meta-network \(\mathcal{M}\) to produce a function embedding \(z^{func}\), which is processed by the hyper network \(\mathcal{H}\) to parameterize a function \(F_{z^{func}}\), which attempts to compute the transformation on probe inputs (used to encourage the system to generalize). However, our approach goes beyond basic meta-learning. The function embedding \(z^{func}\) can then be seen as a single input or output at the next level of abstraction, when the same networks \(\mathcal{M}\) and \(\mathcal{H}\) are used to transform function embeddings based on examples of a meta-mapping (b). To evaluate meta-mapping performance, a probe embedding of a held-out function is transformed by the architecture to yield a predicted embedding for the transformed task. The performance of this predicted embedding is evaluated by moving back down a level of abstraction and evaluating on the actual target task (c). Because the function embedding is predicted by a transformation rather than from examples, new tasks can be performed zero-shot. (\(M\) and \(H\) are learnable deep networks, and $F_{z}$ is a deep network parameterized by $\mathcal{H}$ conditioned on function embedding \(z\). Input and output encoders/decoders are omitted for simplicity. See the text and Appendix \ref{app_model_details} for details.)} \label{architecture_inference_fig}
\end{figure}
\end{block}
\end{column}
\begin{column}[t]{0.248\textwidth}
\begin{block}{\huge Why \& prior work}
\begin{itemize}
\item Prior work has considered zero-shot task performance from language descriptions, with approaches that implicitly use prior task knowlege for the novel task.
\item However, transforming a task representation provides a richer and more explicit way to use prior knowledge.
\item Probably because of this, meta-mapping offers better zero-shot performance than a baseline of performing the task from natural language alone.
\item Meta-mapping thus offers a happy intermediate between meta-learning (which requires data on the new task), and zero-shot performance from language alone.
\end{itemize}
\begin{figure}[H]
\centering
\includegraphics[width=0.9\textwidth]{../figures/why_meta_mapping.png}
\label{fig_why_meta_mapping}
\end{figure}

\end{block}
\begin{block}{\huge Conclusions}
\end{block}
\end{column}
\end{columns}
\end{frame}
\end{document}
